---
title: "Introduction to calibration with gmish"
author: "Gary Weissman"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Visualizing calibration}
  %\usepackage[UTF-8]{inputenc}
---

# This will be a vignette for the calibration plot examples

First, let's train two models on the same data set.

```{r}
library(gmish)
library(randomForest, quiet = TRUE)

dd <- ggplot2::diamonds
dd$exp <- dd$price > 5000
dd$price <- NULL

m1 <- glm(exp ~ ., data = dd, family = 'binomial')
p1 <- predict(m1, type = 'response')

m2 <- randomForest(as.factor(exp) ~ ., data = dd, ntrees = 50)
p2 <- predict(m2, type = 'prob')[,2]

```

Now we can see the predictions from both models.

```{r preds}
res <- data.frame(obs = dd$exp, glm = p1, rf = p2)
head(res)
```

Now let's examine the calibration of each model in predicting the same outcome. We can use this easy formula interface.

```{r calib}
# First look at glm model
calib_plot(obs ~ glm, res, cut = 10)
# Then look at RF model
calib_plot(obs ~ rf, res, cut = 10)

# Sometimes it's helpful to add a best fit line (linear model)
calib_plot(obs ~ rf, res, cut = 10, fitline = TRUE)

# Sometimes it's helpful to add a smoothed fit line (loess)
calib_plot(obs ~ rf, res, cut = 10, smooth = TRUE)

```

Sometimes it's helpful to look at the distribution of the probabilities. So let's add a rug plot.

```{r more feats}
# Now look at both models at the same time
calib_plot(obs ~ glm + rf, res, cut = 10)
# Show rug
calib_plot(obs ~ glm + rf, res, cut = 10, rug = TRUE)
```

And sometimes we may want to increase or decrease the number of bins.

```{r bins}
# Fewer bins
calib_plot(obs ~ glm, res, cut = 5)
# More bins
calib_plot(obs ~ glm, res, cut = 20)
# And change the color for fun because calib_plot returns a ggplot object
calib_plot(obs ~ glm + rf, res, cut = 10) + ggplot2::scale_color_viridis_d()
```

And sometimes there may be multiple outcomes *and* multiple models. Here is a multi-class calibration plot. This approach may be helpful when you want to plot the calibration of a single model among subgroups.

```{r multi}
# first create a new model with a different outcome
dd2 <- ggplot2::diamonds
dd2$exp2 <- dd2$price > 4000
dd2$price <- NULL

m3 <- glm(exp2 ~ ., data = dd2, family = 'binomial')
p3 <- predict(m3, type = 'response')

res2 <- data.frame(obs1 = dd$exp, obs2 = dd2$exp2, glm1 = p1, glm2 = p3)
head(res2)

# Now use the formula interface to plot each outcome (LHS) against each prediction (RHS)
# in the order that they correspond
mc_calib_plot(obs1 + obs2 ~ glm1 + glm2, data = res2)

```
